Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations

### 2025-02-03 draft.tex
new table entries, completed, abbreviated

>>>>

\section{Updated Tables}

\begin{table}[t]
    \centering
    \begin{tabular}{|c||c|c|c|c|c||c|c|c|}
        \hline
                        & $\grad$ ref  & $\grad$ est & $\grad$ ratio       & $\grad$ est   & $\grad$ ratio      & $\divergence$ ref  & $\divergence$ est  & $\divergence$ ratio \\ 
        \hline
        $\calT_{Q}$     & 0.318        & 0.9040624834 & 2.842963784        & 0.904062477   & 2.84296376         & 0.225              & 1.339553527        & 5.95357123111   \\
        \hline
        $\calT_{L}$     & 0.822        & 2.381225711 & 2.896868261         & 1.421249625   & 1.72901414234      & 0.322              & 2.505543143        & 7.78118988509   \\
        \hline
        $\calT_{L'}$    & 0.822        & 2.391924501 & 2.909883821         & 2.391924492   & 2.90988381022      & 0.322              & 4.053039867        & 12.5870803323   \\
        \hline
        $\calT_{S,5}$   & 0.978        & 2.752696283 & 2.81461787627       & 1.779367097   & 1.81939375971      & 0.346              & 3.717588832        & 10.7444763931   \\ 
        \hline % centered
        $\calT_{S'}$    & 0.978        & 3.131764309 & 3.2022129948        & 3.131764307   & 3.20221299284      & 0.346              & 5.453759801        & 15.7623115636   \\
        \hline % non-centered
        $\calT_{S''}$   & 0.978        & 2.761956509 & 2.82408641002       & 2.761956506   & 2.82408640695      & 0.346              & 4.662992222        & 13.4768561329   \\
        \hline
    \end{tabular}
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 2D domains.
    Reference values for the gradient and divergence (2nd and 7th column) computed with finite element methods together with estimates and ratios: 
    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column), 
    and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (8th and 9th column).
    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
    }\label{table:estimates2D}
\end{table}

\begin{table}[t]
    \color{red}
    \centering
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
        \hline
                        & $\grad$ ref  & $\grad$ est  & $\grad$ ratio       & $\grad$ est & $\grad$ ratio  \\
        \hline
        $\calT_{C,5}$   & 0.3179254398 & 4.31776537   & 13.5810628200       & 3.246136642  & 10.214410571  \\
        \hline
        $\calT_{C,K}$   & 0.3177997026 & 3.571616557  &  11.238577405       & 11.03485346  & 34.722667673  \\
        \hline
        $\calT_{B,5}$   & 1.022627161  & 7.698889039  & 7.52853956223       & 25.97226447  & 25.397589131  \\
        \hline
        $\calT_{B,K}$   & 1.022627161  & 10.10602558  & 9.88241459391       & 53.76320901  & 52.573617306  \\
        \hline
        $\calT_{F}$     & 0.7117133306 & 10.62410979  & 14.9275127122       & 269.5329306  & 378.70996511  \\ 
        \hline
    \end{tabular} 
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants of the gradient over various triangulated 3D domains.
    Reference values for the gradient (2nd column) computed with finite element methods together with estimates and ratios: 
    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column).
    }\label{table:estimates3D:grad}
\end{table}

\begin{table}[t]
    \color{red}
    \centering
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
        \hline
                        & $\curl$ ref  & $\curl$ est & $\curl$ ratio     & $\divergence$ ref & $\divergence$ est & $\divergence$ ratio \\ 
        \hline
        $\calT_{K,5}$   & 0.2250062929 & 141.1488115 & 627.310506212     & 0.1837655124      & 3.391164992       & 18.4537617952   \\
        \hline
        $\calT_{C,K}$   & 0.2250695032 & 12.15727753 & 54.0308334194     & 0.1837881324      & 25.89943821       & 140.920079397   \\
        \hline
        $\calT_{B,5}$   & 0.3315710272 & 113.0845771 & 341.056871148     & 0.2330604743      & 152.8861269       & 655.993374077   \\
        \hline
        $\calT_{B,K}$   & 0.3315710272 & 162.6872182 & 490.655711308     & 0.2330604743      & 512.2731352       & 2198.02665698   \\
        \hline
        $\calT_{F}$     & 0.5549678737 & 25752.34203 & 46403.3023359     & 0.3106774562      & 8958.467291       & 28835.2666478   \\ 
        \hline
    \end{tabular}
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 3D domains.
    Reference values for the curl and divergence (2nd and 5th column) computed with finite element methods together with estimates and ratios
    that rely on Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (3rd and 4th column) and with $k=1$ (5th and 6th column).
    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
    }\label{table:estimates3D:curldiv}
\end{table}
